---
author: "Sebastian Gibb, University Medicine Greifswald"
title: "`topdownr` - Systematic Optimisation of Protein Sequencing for Top-Down Proteomics"
subtitle: ""
date: "2017-12-05"
output:
  beamer_presentation:
    keep_tex: no
    theme: metropolis
    slide_level: 1
    incremental: no
    md_extensions: -implicit_figures
fontsize: 10pt
classoption: compress
header-includes:
    \hypersetup{colorlinks,citecolor=orange,filecolor=orange,linkcolor=orange,urlcolor=orange}
    \usepackage[T1]{fontenc}
    \usepackage{chemfig}
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE, fig.height=5, collapse=TRUE, comment="#")
```

```{r, topdownrsetup, include=FALSE}
suppressPackageStartupMessages(library("topdownr"))
suppressPackageStartupMessages(library("topdownrdata"))
suppressPackageStartupMessages(library("ranger"))

## the mass adduct for a proton
H <- 1.0078250321

myoglobin <- readTopDownFiles(
    path = topdownrdata::topDownDataPath("myoglobin"),
    type = c("a", "b", "c", "x", "y", "z"),
    ## adducts (add -H/H to c/z and name
    ## them cmH/zpH (c minus H, z plus H)
    adducts = data.frame(
        mass=c(-H, H),
        to=c("c", "z"),
        name=c("cmH", "zpH")),
    modifications = "Met-loss",
    neutralLoss = NULL,
    tolerance = 5e-6
)
myoglobin <- filterCv(myoglobin, threshold=30)
myoglobin <- filterInjectionTime(myoglobin, maxDeviation=log2(3))
myoglobin <- filterIntensity(myoglobin, threshold=0.1)
myoglobin <- filterNonReplicatedFragments(myoglobin)
myoglobin <- aggregate(myoglobin)
myoglobinNcb <- as(myoglobin, "NCBSet")
## number of fragments
nFragments <- summary(myoglobin)$Fragments

## features of interest
foi <- c(
    "AgcTarget",
    "EtdReagentTarget",
    "EtdActivation",
    "CidActivation",
    "HcdActivation"
)

rfTable <- as.data.frame(cbind(
    scale(as.data.frame(colData(myoglobin)[foi])),
    Fragments = nFragments
))

featureImportance <- ranger(
    Fragments ~ .,
    data = rfTable,
    importance = "impurity"
)$variable.importance
```

# Fragmentation Notation

\centering
\input{images/abcxyzmn.tex}

# Workflow (simplified)

\makebox[0.85\paperwidth][c]{
\input{images/topdownr-workflow-simplified.tex}
}

# Fragmentation Map

```{r fragmentationMap, echo=FALSE, fig.height=10, fig.width=15}
sel <-
    myoglobin$Mz == 707.3 &
    myoglobin$AgcTarget == 1e6 &
    myoglobin$EtdReagentTarget == 1e7

myoglobinNcbSub <- myoglobinNcb[, sel]

fragmentationMap(
    myoglobinNcbSub,
    nCombinations = 10,
    labels = substring(colnames(myoglobinNcbSub), 26, 38)
)
```

# Important Settings

```{r featureImportance, echo=FALSE, fig.height=10, fig.width=15}
barplot(
    featureImportance/sum(featureImportance),
    cex.names = 1.65,
    col = c("#E2E2E2", "#E2E2E2", "#23373B", "#E2E2E2", "#23373B"),
    border = NA
)
```

# Collaborative Work

Thank you for your attention!

```{r, eval=FALSE}
biocLite("topdownr")
```

github: [\@sgibb](https://github.com/sgibb) /
twitter: [\@sebastiangibb](https://twitter.com/sebastiangibb)

- Pavel V. Shliaha.
- Vladimir Gorshkov.
- Ole Nørregaard Jensen.
- Malena Schack Jespersen.
- Veit Schwämmle.

(this talk: https://github.com/sgibb/EuroBioc2017-topdownr/)
